%-------------------------
% Resume in Latex
% Author : Adithya R Ganesh
%------------------------

\documentclass[11pt,letter]{article}
\newcommand\tab[1][1cm]{\hspace*{#1}}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{setspace}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}
\newcommand{\resItem}[1]{ \vspace{-1pt}
  \item\small{
     
  } \vspace{-1pt}
}
\newcommand{\ac}[3]{
  \small{
    {#1}\tab{\textbf{#2:} #3 \vspace{-2pt}}
    \\*
  }
}
\newcommand{\ach}[2]{
  \small{
    \textbf{#1}{: #2 \vspace{-2pt}}
    \\*
  }
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-4pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\small #2} \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-5pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \singlespacing
\begin{document}

%----------HEADING-----------------

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\LARGE Adithya Raghu Ganesh} &  \href{mailto:araghug@ncsu.edu}{araghug@ncsu.edu}\\
  \href{https://www.linkedin.com/in/adithyarganesh}{LinkedIn} \href{https://www.github.com/adithyarganesh}{, GitHub}
  \href{https://www.kaggle.com/adithyarganesh}{, Kaggle}& 516-373-9301 \\
   \vspace{-19pt}
%   {2215B Gorman St, Raleigh, NC 27606} 
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {North Carolina State University}{Raleigh}
      {Master of Computer Science \textbf{GPA 3.5/4}}{Aug. 2019 - Present}
    \resumeSubheading
      {SSN College of Engineering, Anna University}{Chennai}
      {B Tech. Information Technology  \textbf{CGPA 8.09/10 }}{May. 2019}
    \resumeSubheading
      {Indian Statistical Institute}{Kolkata}
      {\href{https://www.isical.ac.in/~ecsu/SelectedApplicants.pdf}{Summer School on Computer Vision, Graphics and Image Processing}}{May. 2017}
  \resumeSubHeadingListEnd

%-----------PROFESSIONAL---------------
\section{Internship/Professional Experience}
  \resumeSubHeadingListStart
   \resumeSubheading
      {Computer Vision Team }{Sep. 2018 - Mar. 2019}
      {Iteron Group }{Remotely for Switzerland}
      \resumeItemListStart
        \resItem {}
          {Built a fine grained hierarchical classifier for animal classification (Zoo Usecase). Classified different animals defined by upper hierarchy and also classified animals within homogeneous classes defined as lower hierarchy.}
    \resumeItemListEnd
    \resumeSubheading
      {Platform Development Intern}{May. 2018 - Jul. 2018}
      {Imagin8ors Pte. Ltd.}{Chennai}
      \resumeItemListStart
        \resItem {}
          {Coded various optimized Python algorithms to map different question types and answers. Other duties include audio stitching, code refactoring and research on Stanford Natural Language Processing. Designed a seq2seq model for a recommendation engine to automate challenges based on competency.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
%-----------RESEARCH EXPERIENCE-----------------
\section{Research Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Guiding eyes for the blind}{Sep. 2019 - Present}
      {North Carolina State University}{Raleigh}
      \resumeItemListStart
        \resItem{Optimization}
          {Modelling a network to determine the behaviour of dogs to different stimuli and observing its movements in an area.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Location, Detection and Navigation of an Unmanned Marine Vehicle}{Nov. 2017 - Jan. 2018}
      {Indian Institute of Technology Madras}{Chennai}
      \resumeItemListStart
        \resItem{Optimization}
          {Modelled a prototype for an Indoor Positioning System. Found an alternative approach using clustering algorithms to determine vehicle’s position from ultrasonic sensor data thereby improving system accuracy by 5\%. Incorporated a real time object detection model for marine vehicle collision avoidance.}
      \resumeItemListEnd

    \resumeSubheading
      {A Non-Invasive Approach for Prediction of Hemoglobin Value in Blood}{May. 2017 - Jul. 2017}
      {Indian Statistical Institute}{Kolkata}
      \resumeItemListStart
        \resItem{Machine Learning}
          {Led a team generating a solution to integrate optical recognition of chromatic changes in a palm by extracting features from a video sequence using Time Series Analysis and Eulerian Magnification. Applied mathematical regression models to predict hemoglobin value with an 80.7\% accuracy.}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd

%-------------Publications-----------------
\section{Publications}
    \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://ieeexplore.ieee.org/document/8851800}{DICENet: Fine-Grained Recognition via Dilated Iterative Contextual Encoding}}{Jul. 2019}
      {International Joint Conference on Neural Networks (IJCNN 2019)}{Hungary}
    \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Algorithms}
      {Developed a heuristic search model to determine the moves to unscramble the Rubik's globe puzzle.}
      \resumeSubItem{Keypoints detection}
      {Annotated images and used tensorflow libraries to detect leaf tips and collars in images.}
    \resumeSubItem{Cloud Computing}
      {Devised an end-to-end cloud based e-commerce solution with a recommender engine. Presented this prototype in ``14th International Conference on Distributed Computing and Internet Technology".}
    \resumeSubItem{Machine Learning}{Ranked 1st in the hackathon conducted by Mahindra \& Mahindra. Pre-processed the unstructured dataset given and developed a model that gave the best accuracy while testing on unknown test data.}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
     \textbf{Languages: }{Python, SQL, Java, C++, C  }
     \hfill
     \break
     \textbf{Python libraries: }{TensorFlow, Keras, Pandas, OpenCV, Scrapy }
   
% \section{Achievements}
%     \ac
%     {2018} {1st Rank}
%     {Mahindra \& Mahindra Machine Learning Hackathon}
    % \ach 
    % {2018\tab Certificate of Appreciation}
    % {Project presentation - 14th ICDCIT – Springer International Conference}
    % \ac 
    % {2017}{Best Project Presentation}
    % {Non-invasive approach for prediction of hemoglobin value in blood}
    % \ac
    % {2017}{2nd Place}
    % {Math Quiz, Symposium at Madras Institute of Technology, Chennai}
    % \ach
    % {2016\tab Sanction letter}{Internal Funded Project - Quick Basket}
    % \ach 
    % {2015\tab 2nd rank}
    %   {CBSE examination - Science Group with Informatics Practices}
    % \ac
    % {2015}{Certificate of Appreciation}
    %   {Top 1\% of students in 12th CBSE exams, Issued by Union HRD Minister of India}



\section{Organizations \& Activities}
    % \ach
    %     {Organizing Committee}
    %     {``Technology Awareness program on AI" \& ``2 day workshop on AI and ML"}
    \ach
        {Student Volunteer}
        {``Teach a School Program" - Taught Mathematics and English to underprivileged students}
%     \ach
%         {Head}
%         {``Entrepreneurship and Development Cell" and ``Model United Nations" at my college}
%-------------------------------------------
\end{document}
